### 2018-04-04 Sections/economics_of_the_quantum_internet.tex
minor

\begin{table*}[!htb]
\caption{Summary of the dynamics of various economic models under several computational scaling functions of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\text{global}=\sum_{j\in \text{nodes}} n_j$} qubits in the global network.\comment{Complete}} \label{tab:summary_ec_models}
\begin{tabular}{|p{0.255\linewidth}|p{0.22\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|}
	\hline
	\[\text{Model}\] & \[\text{General form}\] & \[f_\text{sc}(n)=n^{}\] & \[f_\text{sc}(n)=n^p\] & \[f_\text{sc}(n)=e^n\]\\
	\hline \hline
	Network price scaling factor (Sec.~\ref{sec:NPSF}) & \[\chi_\text{sc}(n)=\frac{f_\text{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\
	\hline
	Spot price of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_0=\frac{e^{-\gamma_\text{ror}} C_0}{\chi_\text{sc}(N_0)}\] & &  & \\
	\hline
	Future cost of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_t=\frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)}
\] &  &  & \\
	\hline
	Time-share computational power (Sec.~\ref{sec:arb_free_time_share}) & \[c_n=n \cdot \chi_\text{sc}(n_\text{global})
\] & \[n\] & \[n\cdot{n_\text{global}}^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}}\]\\
	\hline
	Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(n)}\] & \[1\] & \[\left(\frac{n_\text{global}}{n}\right)^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}e^n}\]\\
	\hline
	Single qubit leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_\text{qubit}=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}\] & \[1\] & \[{n_\text{global}}^{p-1}\] & \[\frac{e^{n_\text{global}-1}}{n_\text{global}}\]\\
	\hline
	Time-dependent leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n(t)=\frac{\chi_\text{sc}(N_0{\gamma_N}^t)}{\chi_\text{sc}(n)}\] &  \[1\] & \[\left(\frac{N_0{\gamma_N}^t}{n}\right)^{p-1}\] & \[\frac{n \cdot \text{exp}(N_0{\gamma_N}^t)}{N_0{\gamma_N}^t e^n}\]\\
	\hline
	Forward contract price (Sec.~\ref{sec:for_contr}) & \[F_T=\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{\chi_\text{sc}(N_0 {\gamma_N}^T)}\]
 &  & & \\
	\hline
	Tax performance multiplier (Sec.~\ref{sec:taxation}) & \[M(N_\text{tax})=\frac{f_\text{sc}(N_\text{tax})}{f_\text{sc}(N_\text{tax} \gamma_T)}\] & \[{\gamma_T}^{-1}\] & \[{\gamma_T}^{-p}\] & \[e^{N_\text{tax}(1-\gamma_T)}\]\\
	\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[!htb]
\caption{Summary of the dynamics of various economic models under several computational scaling functions of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\text{global}=\sum_{j\in \text{nodes}} n_j$} qubits in the global network.\comment{Complete}} \label{tab:summary_ec_models}
\begin{tabular}{|p{0.255\linewidth}|p{0.22\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|}
	\hline
	\[\text{Model}\] & \[\text{General form}\] & \[f_\text{sc}(n)=n^{}\] & \[f_\text{sc}(n)=n^p\] & \[f_\text{sc}(n)=e^n\]\\
	\hline \hline
	Network price scaling factor (Sec.~\ref{sec:NPSF}) & \[\chi_\text{sc}(n)=\frac{f_\text{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\
	\hline
	Spot price of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_0=\frac{e^{-\gamma_\text{ror}} C_0}{\chi_\text{sc}(N_0)}\] & &  & \\
	\hline
	Future cost of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_t=\frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)}
\] &  &  & \\
	\hline
	Time-share computational power (Sec.~\ref{sec:arb_free_time_share}) & \[c_n=n \cdot \chi_\text{sc}(n_\text{global})
\] & \[n\] & \[n\cdot{n_\text{global}}^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}}\]\\
	\hline
	Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(n)}\] & \[1\] & \[\left(\frac{n_\text{global}}{n}\right)^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}e^n}\]\\
	\hline
	Single qubit leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_\text{qubit}=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}\] & \[1\] & \[{n_\text{global}}^{p-1}\] & \[\frac{e^{n_\text{global}-1}}{n_\text{global}}\]\\
	\hline
	Time-dependent leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n(t)=\frac{\chi_\text{sc}(N_0{\gamma_N}^t)}{\chi_\text{sc}(n)}\] &  \[1\] & \[\left(\frac{N_0{\gamma_N}^t}{n}\right)^{p-1}\] & \[\frac{n e^{N_0{\gamma_N}^t-n}}{N_0{\gamma_N}^t}\]\\
	\hline
	Forward contract price (Sec.~\ref{sec:for_contr}) & \[F_T=\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{\chi_\text{sc}(N_0 {\gamma_N}^T)}\]
 &  & & \\
	\hline
	Tax performance multiplier (Sec.~\ref{sec:taxation}) & \[M(N_\text{tax})=\frac{f_\text{sc}(N_\text{tax})}{f_\text{sc}(N_\text{tax} \gamma_T)}\] & \[{\gamma_T}^{-1}\] & \[{\gamma_T}^{-p}\] & \[e^{N_\text{tax}(1-\gamma_T)}\]\\
	\hline
\end{tabular}
\end{table*}
